Comparing the Enriched Hits of Different Probes

### 2025-02-07 LipidProbe/EnrichedHitsComparison.qmd
big issue in data wrangling -- fixed now'

<!-- Data wrangling, will comment out most of this when it's all done. 
Pulling the enriched hits from each probe, then making a long dataframe that can be plopped into a Venn diagram adjacent visualization -->
```{r setup, echo=FALSE,include=FALSE}
library(dplyr)
library(tidyr)
library(readr)
library(ggvenn)
library(crosstalk)
library(VennDiagram)
library(htmlwidgets)
library(plotly)
library(DT)
# # Making a big shared dataset with all of the TMT-quantified lipid probes - this is a little hand-wavey because some were run at different times... TBD if we want to keep this.
# PA_data <- read_csv("LipidProbe/DataSets/PA_HeLa_AT_2025.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)

# PE_data <- read_csv("LipidProbe/DataSets/PE_HeLa_AT_2025.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)

# Spa_data <- read_csv("LipidProbe/DataSets/Spa_Huh7_SF_2024.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)

# Sph_data <- read_csv("LipidProbe/DataSets/Sph_Huh7_SF_2024.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)

# FA_8_3_data <- read_csv("LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)

# FA_1_10_data <- read_csv("LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)

#write.csv(combinedDataset, "LipidProbe/DataSets/combinedProbeDatasets_TMT.csv")
```

>>>>

<!-- Data wrangling, will comment out most of this when it's all done. 
Pulling the enriched hits from each probe, then making a long dataframe that can be plopped into a Venn diagram adjacent visualization -->
```{r setup, echo=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(readr)
library(ggvenn)
library(crosstalk)
library(VennDiagram)
library(htmlwidgets)
library(plotly)
library(DT)
# Making a big shared dataset with all of the TMT-quantified lipid probes - this is a little hand-wavey because some were run at different times... TBD if we want to keep this.

PA_data <- read_csv("LipidProbe/DataSets/PA_HeLa_AT_2025.csv") |>
	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue) |>
  mutate(fdr = "Data not available")

PE_data <- read_csv("LipidProbe/DataSets/PE_HeLa_AT_2025.csv") |>
	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue) |>
  mutate(fdr = "Data not available")

Spa_data <- read_csv("LipidProbe/DataSets/Spa_Huh7_SF_2024.csv") |>
	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)

Sph_data <- read_csv("LipidProbe/DataSets/Sph_Huh7_SF_2024.csv") |>
	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)

FA_8_3_data <- read_csv("LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv") |>
	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)

FA_1_10_data <- read_csv("LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv") |>
	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)

combinedDataset <- rbind(PA_data, PE_data, Spa_data, Sph_data, FA_8_3_data, FA_1_10_data)

# write.csv(combinedDataset, "LipidProbe/DataSets/combinedProbeDatasets_TMT.csv")

write.csv(combinedDataset, "/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/SearchByProtein/combinedProbeDatasets_TMT.csv")
```
